### 2015-05-24 docs/report/array_partitioning.tex
Renamed array sharing to array partitioning

\section{Array sharing}

As explained in section~\ref{sec:serialization-and-transference} of this document, transferring \ttarray{} objects to and from workers requires the use of \code{Transferable}s to achieve acceptable performance. Since our library will receive \ttarray{} objects to be partitioned and handed over to multiple workers, it is important that it takes as little time as possible for the partitioning of the arrays.\footnote{This does not apply to \tstarray{}s as those can be transferred without being partitioned}

>>>>

\section{Array partitioning}

As explained in section~\ref{sec:serialization-and-transference} of this document, transferring \ttarray{} objects to and from workers requires the use of \code{Transferable}s to achieve acceptable performance. Since our library will receive \ttarray{} objects to be partitioned and handed over to multiple workers, it is important that it takes as little time as possible for the partitioning of the arrays.\footnote{This does not apply to \tstarray{}s as those can be transferred without being partitioned.}
